Reply to reviewers\\ LMCS \#\,6784 Manuscript: \\``Compositional equivalences based on Open pNets''

### 2021-10-22 2016-Weak-FH-Bisim/2021-09-letter2Reviewers.tex
small pass letter

l -6: why not use an asymmetric symbol instead of $\otimes$? 
%QUESTION: veut on vraiment changer de symbole?
A%NSWER:
\begin{quote}
$\otimes$ is a form of composition: we have changed for something similar to the functional composition symbol $\circ$, renamed it into $\odot$
\end{quote}

>>>>

l -6: why not use an asymmetric symbol instead of $\otimes$? 
%QUESTION: veut on vraiment changer de symbole?
A%NSWER:
\begin{quote}
$\otimes$ is a form of composition: we have changed for something similar to the functional composition symbol $\circ$, we chose the $\odot$ symbol and hope it is less confusing
\end{quote}
